---
title: "Figures"
output: html_document
date: "2025-11-18"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ggpubr)
library(ComplexHeatmap)
library(survival)
library(survminer)
library(reshape2)
library(enrichplot)
library(dplyr)
library(extrafont)
library(ggrepel)
library(tidyr)
library(BSgenome.Hsapiens.NCBI.GRCh38)
library(BSgenome)
library(stringr)
library(ggmsa)
library(ggVennDiagram)
library(clusterProfiler)
library(ggh4x)
library(org.Hs.eg.db)
extrafont::loadfonts()
```

#Gene Expression Volcano-Panc
```{r}
rm(list=ls())
res_df<-read.table("sh_vs_ctrl_Pan.txt",header=T)

##Volcano Plot
cols <- c("up" = "#C23D69", "down" = "#20A4F3", "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 1, "down" = 1, "ns" = 0.5)

sig_up_genes <- res_df %>%
  dplyr::filter(Genes %in% c("ENSG00000119953"))

Up_genes<-as.character(length(which(res_df$gene_type=="up")))
Down_genes<-as.character(length(which(res_df$gene_type=="down")))

volcano<-res_df %>%
  ggplot(aes(x = log2FoldChange,
             y = -log10(padj),
             fill = gene_type,
             color=gene_type,
             size = gene_type,
             alpha =gene_type)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(log2(0.5), log2(2)),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-4,-2,-0,2,4),       
                     limits = c(-5.5, 5.5))+
  theme_classic()+
  geom_text(x=-4, y=70, label=paste("Down \n",Up_genes,sep=""),color="black",size=2)+
  geom_text(x=4, y=70, label=paste("Up \n",Down_genes,sep=""),color="black",size=2)+
  geom_text_repel(data = sig_up_genes, # Add labels last to appear as the top layer  
                  aes(label = Gene_Sym),
                  size=2,
                  nudge_y = 1,
                  nudge_x = -2,
                  color="black")+
  geom_point(data = sig_up_genes,shape = 21,alpha=1, fill = "#D5732E",colour = "black")+
  theme(legend.position = "none",
        axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("Figures/Pan_DESEQ_Volcano.png",width=1.5,height=1.5)


#
up <-enrichGO(gene          = res_df$Genes[which(res_df$gene_type=="up")],
                 OrgDb         = org.Hs.eg.db,
                 keyType       = 'ENSEMBL',
                 ont           = "BP",
                 pAdjustMethod = "BH",
                 universe     = res_df$Genes,
                 pvalueCutoff  = 0.05,
                 qvalueCutoff  = 0.05)

up@result<-up@result[which(up@result$ID %in% c("GO:0090132","GO:0001667","GO:0030198","GO:0098742")),]
dotplot(up,font.size = 8)+
  scale_size_area(max_size = 3)+
  theme_classic()+
  theme(legend.position = "right",
        axis.text=element_text(size=8, color="black"),
        axis.text.x=element_text(size=8, color="black"),
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("Figures/Panc_GO_up.pdf",width=4,height=2)
```

#GSEA-Panc
```{r}
rm(list=ls())
GSEA_Pos<-read.table("gsea_report_for_na_pos_1691179573388.tsv",sep="\t",header=T)
GSEA_Neg<-read.table("gsea_report_for_na_neg_1691179573388.tsv",sep="\t",header=T)
df<-rbind(GSEA_Pos,GSEA_Neg)
df$NAME=gsub("HALLMARK_","",df$NAME)
df$NAME[which(df$NAME=="EPITHELIAL_MESENCHYMAL_TRANSITION")]<-"EMT"
df$color<-"grey"
df$color[which(df$FDR.q.val<0.05 & df$NES>0)]<-"#C23D69"
df$color[which(df$FDR.q.val<0.05 & df$NES<0)]<-"#20A4F3"

sig_genes <- df %>%
  dplyr::filter(NAME %in% c("G2M_CHECKPOINT","EMT","KRAS_SIGNALING_DN"))
sig_genes$NAME=gsub("_","\n",sig_genes$NAME)

ggplot(df, aes(NES, -log10(FDR.q.val))) + 
  geom_point(aes(col=color)) + 
  scale_color_identity()+
  coord_cartesian(xlim = c(-7, 7)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = -log10(0.05), linetype = "dashed",color="gray") +
  geom_vline(xintercept = c(-1, 1), linetype = "dashed",color="gray") +
  geom_point(data = sig_genes,shape = 21,alpha=1,colour = "black")+
  geom_text_repel(data = sig_genes[which(sig_genes$NES>0),], 
                  aes(label = NAME),
                  force = 1,
                  size=1.5,
                  nudge_y =0,
                  nudge_x = 5)+
  geom_text_repel(data = sig_genes[which(sig_genes$NES<0),], 
                  aes(label = NAME),
                  force = 1,
                  size=1.5,
                  nudge_y = 0.5,
                  nudge_x = -2)+
  labs(x="NES", y="-log10 FDR") +
  theme_classic() +
  theme(axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank())
ggsave("Figures/GSEA_Pan.pdf",width=1.5,height=1.5)
```

#Gene Expression Volcano-Ov
```{r}
rm(list=ls())
res_df<-read.table("sh_vs_ctrl_Ov.txt",header=T)

##Volcano Plot
cols <- c("up" = "#C23D69", "down" = "#20A4F3", "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 1, "down" = 1, "ns" = 0.5)

sig_up_genes <- res_df %>%
  dplyr::filter(Genes %in% c("ENSG00000119953"))

Up_genes<-as.character(length(which(res_df$gene_type=="up")))
Down_genes<-as.character(length(which(res_df$gene_type=="down")))

volcano<-res_df %>%
  ggplot(aes(x = log2FoldChange,
             y = -log10(padj),
             fill = gene_type,
             color=gene_type,
             size = gene_type,
             alpha =gene_type)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(log2(0.5), log2(2)),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-4,-2,-0,2,4),       
                     limits = c(-5.5, 5.5))+
  theme_classic()+
  geom_text(x=-4, y=200, label=paste("Down \n",Up_genes,sep=""),color="black",size=2)+
  geom_text(x=4, y=200, label=paste("Up \n",Down_genes,sep=""),color="black",size=2)+
  geom_text_repel(data = sig_up_genes, # Add labels last to appear as the top layer  
                  aes(label = Gene_Sym),
                  size=2,
                  nudge_y = 1,
                  nudge_x = -2,
                  color="black")+
  geom_point(data = sig_up_genes,shape = 21,alpha=1, fill = "#D5732E",colour = "black")+
  theme(legend.position = "none",
        axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("Figures/Ov_DESEQ_Volcano.png",width=1.5,height=1.5)


#
up <-enrichGO(gene          = res_df$Genes[which(res_df$gene_type=="up")],
                 OrgDb         = org.Hs.eg.db,
                 keyType       = 'ENSEMBL',
                 ont           = "BP",
                 pAdjustMethod = "BH",
                 universe     = res_df$Genes,
                 pvalueCutoff  = 0.05,
                 qvalueCutoff  = 0.05)

up@result<-up@result[which(up@result$ID %in% c("GO:0001525","GO:0022407","GO:0032944")),]
dotplot(up,font.size = 8)+
  scale_size_area(max_size = 3)+
  theme_classic()+
  theme(legend.position = "right",
        axis.text=element_text(size=8, color="black"),
        axis.text.x=element_text(size=8, color="black"),
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("Figures/Ov_GO_up.pdf",width=4,height=2)
```

#GSEA-Ov
```{r}
rm(list=ls())
GSEA_Pos<-read.table("gsea_report_for_na_pos_1691179517599.tsv",sep="\t",header=T)
GSEA_Neg<-read.table("gsea_report_for_na_neg_1691179517599.tsv",sep="\t",header=T)
df<-rbind(GSEA_Pos,GSEA_Neg)
df$NAME=gsub("HALLMARK_","",df$NAME)
df$NAME[which(df$NAME=="EPITHELIAL_MESENCHYMAL_TRANSITION")]<-"EMT"
df$color<-"grey"
df$color[which(df$FDR.q.val<0.05 & df$NES>0)]<-"#C23D69"
df$color[which(df$FDR.q.val<0.05 & df$NES<0)]<-"#20A4F3"

sig_genes <- df %>%
  dplyr::filter(NAME %in% c("EMT","TGF_BETA_SIGNALING","KRAS_SIGNALING_UP"))
sig_genes$NAME=gsub("_","\n",sig_genes$NAME)

ggplot(df, aes(NES, -log10(FDR.q.val))) + 
  geom_point(aes(col=color)) + 
  scale_color_identity()+
  coord_cartesian(xlim = c(-2, 10)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = -log10(0.05), linetype = "dashed",color="gray") +
  geom_vline(xintercept = c(-1, 1), linetype = "dashed",color="gray") +
  geom_point(data = sig_genes,shape = 21,alpha=1,colour = "black")+
  geom_text_repel(data = sig_genes[which(sig_genes$NES>0),], 
                  aes(label = NAME),
                  force = 1,
                  size=1.5,
                  nudge_y =0,
                  nudge_x = 5)+
  geom_text_repel(data = sig_genes[which(sig_genes$NES<0),], 
                  aes(label = NAME),
                  force = 1,
                  size=1.5,
                  nudge_y = 0.5,
                  nudge_x = -2)+
  labs(x="NES", y="-log10 FDR") +
  theme_classic() +
  theme(axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank())
ggsave("Figures/GSEA_Ov.pdf",width=1.5,height=1.5)
```

#GSEA plot
```{r,fig.width=2,fig.height=1.5}
rm(list=ls())
rnk<-read.table("Pan_GSEA_Sorted.rnk")
geneList <- rnk[,2]
names(geneList) <- rnk[,1]
geneList <- sort(geneList, decreasing = TRUE)
gmt <- read.gmt("ancreatic_DESEQ.GseaPreranked.1691179573388/edb/gene_sets.gmt")

gsea_res <- GSEA(geneList = geneList,TERM2GENE = gmt,pvalueCutoff = .05,verbose = FALSE)

m<-gseaplot2(gsea_res,geneSetID = "HALLMARK_KRAS_SIGNALING_DN",pvalue_table = F,
          base_size = 4,rel_heights = c(1.2, 0.2, 0.4),
          color="#C23D69",ES_geom="dot")
ggsave("GSEA_KRAS.pdf",m,height=1.5,width=2)
```

#Splicing Bar plot-Panc
```{r}
rm(list=ls())
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events_Sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_Sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

#Making a BarPplot with the Proportion of Significant Events in both cell line
Event_Count_Pan<-data.frame(table(Pancreatic_Events_Sig$column_label),"PDAC")
Event_Count_Ov<-data.frame(table(Ovarian_Events_Sig$column_label),"HGSOC")
colnames(Event_Count_Pan)<-c("Event","Count","Sample")
colnames(Event_Count_Ov)<-c("Event","Count","Sample")
Event_Counts<-rbind(Event_Count_Pan,Event_Count_Ov)
Event_Counts$Event<-as.character(Event_Counts$Event)
Event_Counts$Event[which(Event_Counts$Event=="SE")]<-"CE"
Event_Counts$Event<-factor(Event_Counts$Event,levels=c("CE","A5SS","A3SS","MXE","RI"))

library(ggplot2)
ggplot(Event_Counts,aes(x=Event,y=Count,fill=Sample))+
  geom_bar(stat="identity", position="dodge",fill="#8AA54E",width=.8)+
  coord_flip()+
  labs(x="",y="# of Events")+
  theme_classic()+
  theme(legend.position =c(0.85, .75),
        legend.text=element_text(size=5),
        legend.title=element_text(size=6),
        axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=6, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())+
  guides(fill=guide_legend(title="Cancer Type"))+
  theme(legend.key.size = unit(0.3, 'cm'))

ggsave("Figures/Common_Events_Distribution_Panc.pdf",width=1.8,height=1.5)
```

#Splicing Bar plot-Ov
```{r}
rm(list=ls())
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("/All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events_Sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_Sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

#Making a Barplot with the Proportion of Significant Events in both cell line
Event_Count_Pan<-data.frame(table(Pancreatic_Events_Sig$column_label),"PDAC")
Event_Count_Ov<-data.frame(table(Ovarian_Events_Sig$column_label),"HGSOC")
colnames(Event_Count_Pan)<-c("Event","Count","Sample")
colnames(Event_Count_Ov)<-c("Event","Count","Sample")
Event_Counts<-rbind(Event_Count_Pan,Event_Count_Ov)
Event_Counts$Event<-as.character(Event_Counts$Event)
Event_Counts$Event[which(Event_Counts$Event=="SE")]<-"CE"
Event_Counts$Event<-factor(Event_Counts$Event,levels=c("CE","A5SS","A3SS","MXE","RI"))
Event_Counts<-Event_Counts[which(Event_Counts$Sample=="HGSOC"),]

library(ggplot2)
ggplot(Event_Counts,aes(x=Event,y=Count,fill=Sample))+
  geom_bar(stat="identity", position="dodge",fill="#BE733E",width=.8)+
  labs(x="",y="# of Events")+
  theme_classic()+
  theme(legend.position =c(0.85, .75),
        legend.text=element_text(size=5),
        legend.title=element_text(size=6),
        axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=6, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())+
  guides(fill=guide_legend(title="Cancer Type"))+
  theme(legend.key.size = unit(0.3, 'cm'))

ggsave("Figures/Common_Events_Distribution_Ov.pdf",width=1.8,height=1.5)
```

#Splicing Bar plot
```{r,fig.width=1.5,fig.height=1.5}
rm(list=ls())
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events_Sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_Sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

#Making a BarPplot with the Proportion of Significant Events in both cell line
Event_Count_Pan<-data.frame(table(Pancreatic_Events_Sig$column_label),"PDAC")
Event_Count_Ov<-data.frame(table(Ovarian_Events_Sig$column_label),"HGSOC")
colnames(Event_Count_Pan)<-c("Event","Count","Sample")
colnames(Event_Count_Ov)<-c("Event","Count","Sample")
Event_Counts<-rbind(Event_Count_Pan,Event_Count_Ov)
Event_Counts$Event<-as.character(Event_Counts$Event)
Event_Counts$Event[which(Event_Counts$Event=="SE")]<-"CE"
Event_Counts$Event<-factor(Event_Counts$Event,levels=c("CE","RI","MXE","A5SS","A3SS"))
Event_Counts$Sample<-factor(Event_Counts$Sample,levels=c("PDAC","HGSOC"))

library(ggplot2)
ggplot(Event_Counts,aes(x=Event,y=Count,fill=Sample))+
  geom_bar(stat="identity", position="dodge",width=.8)+
  labs(x="",y="# of Events")+
  coord_flip()+
  theme_classic()+
  scale_fill_manual(values = c(PDAC="#DFA06E",HGSOC="#5B9CAE"))+
  #coord_flip()+
  theme(legend.position =c(0.85, .85),
        legend.text=element_text(size=5),
        legend.title=element_blank(),
        axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=6, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())+
  guides(fill=guide_legend(title="Cancer Type"))+
  theme(legend.key.size = unit(0.3, 'cm'))

ggsave("Figures/Common_Events_Distribution.pdf",width=1.5,height=1.5)
```

#PSI Correlation
```{r}
rm(list=ls())
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events_Sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_Sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

Events_in_Both<-intersect(Pancreatic_Events_Sig$Identifier,Ovarian_Events_Sig$Identifier)

#Getting Values
Common_Events<-merge(Pancreatic_Events_Sig[c("Identifier","IncLevelDifference")],Ovarian_Events_Sig[c("Identifier","IncLevelDifference")],by="Identifier")
colnames(Common_Events)<-c("Identifier","Pan","Ov")
Common_Events$Color<-"#C0BFBF"
Common_Events$Color[which(Common_Events$Pan>0 & Common_Events$Ov>0)]<-"#C23D69"
Common_Events$Color[which(Common_Events$Pan<0 & Common_Events$Ov<0)]<-"#20A4F3"
SE<-Common_Events[which(sapply(Common_Events$Identifier,function(x){strsplit(x,"_")[[1]][1]})=="SE"),]
  
sig_up_genes <- SE %>%
  dplyr::filter(Identifier %in% c("SE_ENSG00000102882_MAPK3_chr16:30118098-30118163_30117669-30117784_30118348-30118538_-",
                                  "SE_ENSG00000196712_NF1_chr17:31252937-31253000_31248983-31249119_31258343-31258502_+"))

ggplot(SE,aes(x = Pan,y = Ov,color=Color,fill = Color))+
  geom_point(shape = 21,alpha=0.5)+
  scale_fill_identity()+
  scale_colour_identity()+
  labs(x="dPSI PDAC (Ctrl-KD)",y="dPSI HGSOC (Ctrl-KD)")+
  geom_point(data = sig_up_genes,shape = 21,alpha=1, fill = "#D5732E",colour = "black")+
  geom_text_repel(data = sig_up_genes,aes(label = c("italic('MAPK3')","italic('NF1')")),force = 2,nudge_x = -0.25,nudge_y = 0.1,colour = "black",size=2,parse = TRUE)+
  geom_text(data = sig_up_genes,aes(label = c("(ERK1)","")),force = 2,nudge_x = -0.25,nudge_y = 0.02,colour = "black",size=2,parse = TRUE)+
  theme_classic()+
  theme(axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())+
  theme(legend.key.size = unit(1, 'cm'))
ggsave("Figures/2B_Common_SE_Events_PSI.pdf",width=1.5,height=1.5)

ggplot(Common_Events[which(sapply(Common_Events$Identifier,function(x){strsplit(x,"_")[[1]][1]})=="RI"),],aes(x = Pan,y = Ov,color=Color,fill = Color))+
  geom_point(shape = 21,alpha=0.5)+
  scale_fill_identity()+
  scale_colour_identity()+
  labs(x="dPSI PDAC (Ctrl-KD)",y="dPSI OvCa (Ctrl-KD)")+
  #geom_point(data = sig_up_genes,shape = 21,alpha=1, fill = "#D5732E",colour = "black")+
  #geom_text_repel(data = sig_up_genes,aes(label = "MapK3\n(ERK1)"),force = 2,nudge_x = -0.2,nudge_y = 0.1,colour = "black",size=2)+
  theme_classic()+
  theme(axis.text=element_text(size=6, color="black"), 
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())+
  theme(legend.key.size = unit(1, 'cm'))
ggsave("Figures/Common_RI_Events_PSI.pdf",width=1.5,height=1.5)
```

#Overlap Between AS Skipped Exons Events
```{r}
rm(list=ls())
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

#Making a list of SE Genes
CE<-list("PDAC"=Pancreatic_Events$Identifier[which(Pancreatic_Events$column_label=="SE")],
         "HGSOC"=Ovarian_Events$Identifier[which(Ovarian_Events$column_label=="SE")])

ggvenn::ggvenn(CE,fill_color=c("#DFA06E","#5B9CAE"),set_name_size=3,show_percentage=F,text_size=3,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
ggsave("Figures/CE_Overlap.pdf",width=1.5,height=1.25)

#Calcualting significance
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

Pancreatic_Events<-Pancreatic_Events[which(Pancreatic_Events$column_label=="SE"),]
Ovarian_Events<-Ovarian_Events[which(Ovarian_Events$column_label=="SE"),]

#Getting the Significant Events
Pancreatic_Events_sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

ov<-length(intersect(Pancreatic_Events_sig$Identifier,Ovarian_Events_sig$Identifier))
gene_set_1<-length(Pancreatic_Events_sig$Identifier)
universe<-length(unique(c(Pancreatic_Events$Identifier,Ovarian_Events$Identifier)))
gene_set_2<-length(unique(Ovarian_Events_sig$Identifier))

phyper(ov-1,gene_set_1,universe-gene_set_1,gene_set_2,lower.tail=F)


```

#Overlap Between AS Retained Introns Events
```{r}
rm(list=ls())
getwd()
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)

#Getting the Significant Events
Pancreatic_Events<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

#Making a list of SE Genes
RI<-list("PDAC"=Pancreatic_Events$Identifier[which(Pancreatic_Events$column_label=="RI")],"HGSOC"=Ovarian_Events$Identifier[which(Ovarian_Events$column_label=="RI")])

ggvenn::ggvenn(RI,fill_color=c("#DFA06E","#5B9CAE"),set_name_size=3,show_percentage=F,text_size=3,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
ggsave("Figures/2C_RI_Overlap.pdf",width=1.5,height=1.25)



#Calcualting significance
Pancreatic_Events<-read.table("All_Events_Pan.txt",header=T)
Ovarian_Events<-read.table("All_Events_Ov.txt",header=T)


Pancreatic_Events<-Pancreatic_Events[which(Pancreatic_Events$column_label=="RI"),]
Ovarian_Events<-Ovarian_Events[which(Ovarian_Events$column_label=="RI"),]

#Getting the Significant Events
Pancreatic_Events_sig<-Pancreatic_Events[which(Pancreatic_Events$Total_Count_1>=30 & Pancreatic_Events$Total_Count_2>=30 & 
                                                 Pancreatic_Events$PValue<0.05 & Pancreatic_Events$FDR<0.05),]
  
Ovarian_Events_sig<-Ovarian_Events[which(Ovarian_Events$Total_Count_1>=30 & Ovarian_Events$Total_Count_2>=30 &
                                           Ovarian_Events$PValue<0.05 & Ovarian_Events$FDR<0.05),]

ov<-length(intersect(Pancreatic_Events_sig$Identifier,Ovarian_Events_sig$Identifier))
gene_set_1<-length(Pancreatic_Events_sig$Identifier)
universe<-length(unique(c(Pancreatic_Events$Identifier,Ovarian_Events$Identifier)))
gene_set_2<-length(unique(Ovarian_Events_sig$Identifier))

phyper(ov-1,gene_set_1,universe-gene_set_1,gene_set_2,lower.tail=F)
```

#Peak level overlap-Slide4
```{r}
rm(list=ls())
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

Gene_gr<-makeGRangesFromDataFrame(Gene,seqnames.field = "chr",start.field = "start",end.field = "end",strand.field = "strand")
Tag_gr<-makeGRangesFromDataFrame(Tag,seqnames.field = "chr",start.field = "start",end.field = "end",strand.field = "strand")

Gene_gr<-reduce(Gene_gr)
Tag_gr<-reduce(Tag_gr)

ov<-findOverlaps(Gene_gr,Tag_gr)
overlapped<-reduce(c(Gene_gr[queryHits(ov)],Tag_gr[subjectHits(ov)]))
gene_unique<-Gene_gr[-unique(queryHits(ov))]
tag_unique<-Tag_gr[-unique(subjectHits(ov))]


SE<-list("Anti-\nSMNDC1"=c(paste0("A",1:length(overlapped)),paste0("B",1:length(gene_unique))),"Anti-\nHA"=c(paste0("A",1:length(overlapped)),paste0("C",1:length(tag_unique))))

v<-ggvenn::ggvenn(SE,fill_color=c("#936F9B","#FFAAAA"),set_name_size=0,show_percentage=F,text_size=3,fill_alpha=0.9,stroke_size=0.5)+
  coord_cartesian(xlim = c(-1, 1.5), clip = "off")+
  coord_flip() +
  scale_x_reverse()+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        text=element_text(family="Arial", size=0,color="black"))
v
ggsave("Figures/Binding_Regions_peaks.pdf",height=1.5,width=1.1)

```

#Gene level overlap-Slide3
```{r}
rm(list=ls())
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

Gene<-Gene[which(Gene$gene_name=="NF1"),]
Tag<-Tag[which(Tag$gene_name=="NF1"),]


SE<-list("Anti-\nSMNDC1"=Gene$gene_name,"Anti-\nHA"=Tag$gene_name)

v<-ggvenn::ggvenn(SE,fill_color=c("#936F9B","#FFAAAA"),set_name_size=0,show_percentage=F,text_size=3,fill_alpha=0.8,stroke_size=0.5)+
  coord_cartesian(xlim = c(-1, 1.5), clip = "off")+
  coord_flip() +
  scale_x_reverse()+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        text=element_text(family="Arial", size=0,color="black"))
v
ggsave("Figures/Binding_Regions_genes.pdf",height=1.5,width=1.1)


```

#Region combined
```{r,fig.width=3,fig.height=3}
rm(list=ls())
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

Gene_gr<-makeGRangesFromDataFrame(Gene,seqnames.field = "chr",start.field = "start",end.field = "end",
                                  strand.field = "strand",keep.extra.columns = T)

Tag_gr<-makeGRangesFromDataFrame(Tag,seqnames.field = "chr",start.field = "start",end.field = "end",
                                  strand.field = "strand",keep.extra.columns = T)

ov<-findOverlaps(Gene_gr,Tag_gr)
Gene_ov<-Gene_gr[unique(queryHits(ov)),] %>% data.frame()
Gene_ov$feature_type_top<-sapply(Gene_ov$feature_type_top,function(x){strsplit(x,"_")[[1]][1]})

Regions<-table(Gene_ov$feature_type_top) %>% data.frame()
Regions$fraction = Regions$Freq / sum(Regions$Freq)
Regions$ymax = cumsum(Regions$fraction)
Regions$ymin = c(0, head(Regions$ymax, n = -1))
Regions$label_position = (Regions$ymax + Regions$ymin) / 2  # For text positioning
Regions$Label<-paste(Regions$Var1,"=",Regions$Freq,sep="")
my_colors<-c("CDS"="#5AAC56","INTRON"="#4356A1","EXON"="#EFB143","PRIMIRNA"="gray","SS3"="#C7639C","SS5"="#7A5DA0",
       "UTR3"="#42824F","UTR5"="#98C357","SSB"="#FFB6C1")


ggplot(Regions, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect(alpha=.9) +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_label_repel(aes(x = 1, y = label_position, label = Label), max.overlaps = Inf,
                  size = 3.5,force = 1,min.segment.length = 0,fill = scales::alpha("white", 0.6)) +
  theme(legend.position = "none")
ggsave("Figures/Ov_peak_regions.pdf",height=3,width=3)

```

#Region bar plot
```{r,fig.height=1.5,fig.width=1.5}
rm(list=ls())
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

Gene$groups<-"Anti-SMNDC1"
Tag$groups<-"Anti-HA"
df<-rbind(Gene,Tag)
df$feature_type_top<-sapply(df$feature_type_top,function(x){strsplit(x,"_")[[1]][1]})

comb<-df[c("groups","feature_type_top")] %>% gather(groups, feature_type_top) %>% dplyr::count(groups, feature_type_top)
comb$feature_type_top[which(comb$feature_type_top=="PRIMIRNA")]<-"OTHER"
comb$feature_type_top<-factor(comb$feature_type_top,levels=c("CDS","UTR3","UTR5","SS5","SS3","SSB","INTRON","EXON","OTHER"))
comb$groups<-factor(comb$groups,levels=c("Anti-SMNDC1","Anti-HA"))

cls<-c("CDS"="#5AAC56","INTRON"="#4356A1","EXON"="#EFB143","OTHER"="gray","SS3"="#C7639C","SS5"="#7A5DA0",
       "UTR3"="#42824F","UTR5"="#98C357","SSB"="#FFB6C1")

g<-ggplot(comb,aes(x=groups,y=n,fill=feature_type_top))+
  geom_bar(position = "fill",stat = "identity",width=.75,size=1) +
  scale_y_continuous(labels = scales::percent_format())+
  scale_fill_manual(values =cls)+
  theme_classic()+
  labs(x="",y="% of peaks")+
  theme(legend.position = "none",
        axis.text.y=element_text(size=6, color="black"),
        axis.text.x=element_text(size=6, color="black"),
        axis.title = element_text(size=6, color="black"),
        legend.text = element_text(size=6, color="black"),
        panel.background = element_blank(),
        legend.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.height= unit(0.5, 'cm'),
        legend.key.width= unit(0.5, 'cm'))

ggsave("Figures/Binding_Regions.pdf",g,height=1.5,width=1.5)


g2<-g+theme(legend.position = "right")
g2<-cowplot::get_legend(g2)
ggsave("Figures/Binding_Regions_Legend.pdf",g2,height=2,width=1.5)


```


#Gene Ontology
```{r}
rm(list=ls())
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene_sub<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag_sub<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

res_df<-read.table("~/Desktop/Dominguez_Lab/SMNDC1-final/Round1/Summary_Files/sh_vs_ctrl_Pan.txt",header=T)

Gene_go<-enrichGO(gene          = Gene_sub$gene_name,
                 OrgDb         = org.Hs.eg.db,
                 keyType       = 'SYMBOL',
                 ont           = "BP",
                 pAdjustMethod = "BH",
                 universe     = res_df$Gene_Sym,
                 pvalueCutoff  = 0.05,
                 qvalueCutoff  = 0.05)
dotplot(Gene_go)

```

#Regulated genes bound
```{r}
rm(list=ls())

Sum_JC<-function(x){sum(as.numeric(strsplit(x,split = ",")[[1]]))}
Sum_Counts<-function(df){
  df$IJC_Sum_1<-sapply(df$IJC_SAMPLE_1,Sum_JC)
  df$IJC_Sum_2<-sapply(df$IJC_SAMPLE_2,Sum_JC)
  df$SJC_Sum_1<-sapply(df$SJC_SAMPLE_1,Sum_JC)
  df$SJC_Sum_2<-sapply(df$SJC_SAMPLE_2,Sum_JC)
  df$Total_Count_1<-df$IJC_Sum_1+df$SJC_Sum_1
  df$Total_Count_2<-df$IJC_Sum_2+df$SJC_Sum_2
  return(df)
}

SE<-read.table("../Round1/rMATS/Pancreas/SE.MATS.JCEC.txt",header=T)
SE<-Sum_Counts(SE)

#Binding
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

#Getting the Significant Events- GE
SE_Sig<-SE[which(SE$Total_Count_1>=30 & SE$Total_Count_2>=30 & SE$PValue<0.05 & SE$FDR<0.05),]
SE_ov<-list("SE \n Event"=SE_Sig$geneSymbol,"Bound \n Gene"=unique(c(Gene$gene_name,Tag$gene_name)))
ggvenn::ggvenn(SE_ov,fill_color=c("#D5732E","#94B18E"),set_name_size=3,show_percentage=F,
                  text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 2))+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        textt=element_text(family="Arial", size=0,color="black"))
ggsave("Figures/Splicing_bound_ov.pdf",height=1.25,width=1.5)

phyper(346-1,2145,11592-2145,2516,lower.tail=F)


###
SE_sub<-SE_Sig[which(SE_Sig$geneSymbol %in% unique(c(Gene$gene_name,Tag$gene_name))),]
SE_sub$Group<-ifelse(SE_sub$IncLevelDifference>0,"Skipped","Retained")

SE_sub_tab<-data.frame(table(SE_sub$Group))
SE_sub_tab$fraction = SE_sub_tab$Freq / sum(SE_sub_tab$Freq)
SE_sub_tab$ymax = cumsum(SE_sub_tab$fraction)
SE_sub_tab$ymin = c(0, head(SE_sub_tab$ymax, n = -1))
SE_sub_tab$label_position = (SE_sub_tab$ymax + SE_sub_tab$ymin) / 2  # For text positioning
SE_sub_tab$Label<-paste(SE_sub_tab$Var1,"\n=",SE_sub_tab$Freq,sep="")

my_colors<-c("Skipped"="#FE0000","Retained"="#079BF5")
ggplot(SE_sub_tab, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect(alpha=.8) +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 1.4, y = label_position, label = Label), size = 2) +
  theme(legend.position = "none")
ggsave("Figures/Splicing_bound_ov_direction.pdf",height=1.25,width=1.5)

```

#Regulated region bound
```{r}
rm(list=ls())

Sum_JC<-function(x){sum(as.numeric(strsplit(x,split = ",")[[1]]))}
Sum_Counts<-function(df){
  df$IJC_Sum_1<-sapply(df$IJC_SAMPLE_1,Sum_JC)
  df$IJC_Sum_2<-sapply(df$IJC_SAMPLE_2,Sum_JC)
  df$SJC_Sum_1<-sapply(df$SJC_SAMPLE_1,Sum_JC)
  df$SJC_Sum_2<-sapply(df$SJC_SAMPLE_2,Sum_JC)
  df$Total_Count_1<-df$IJC_Sum_1+df$SJC_Sum_1
  df$Total_Count_2<-df$IJC_Sum_2+df$SJC_Sum_2
  return(df)
}

SE<-read.table("../Round1/rMATS/Pancreas/SE.MATS.JCEC.txt",header=T)
SE<-Sum_Counts(SE)

#Binding
Gene<-read.table("Skipper/Peaks/SMNDC1_Gene.reproducible_enriched_windows.tsv",header=T)
Tag<-read.table("Skipper/Peaks/SMNDC1_Tag.reproducible_enriched_windows.tsv",header=T)

Gene<-Gene[which(Gene$q_min<0.05 & Gene$p_min<0.05 & Gene$enrichment_l2or_mean>1),]
Tag<-Tag[which(Tag$q_min<0.05 & Tag$p_min<0.05 & Tag$enrichment_l2or_mean>1),]

regions<-rbind(Gene,Tag)
regions_gr<-makeGRangesFromDataFrame(regions,seqnames.field = "chr",start.field = "start",end.field = "end",strand.field = "strand")


SE_Sig<-SE[which(SE$Total_Count_1>=30 & SE$Total_Count_2>=30 & SE$PValue<0.05 & SE$FDR<0.05),]
SE_region<-makeGRangesFromDataFrame(SE_Sig,seqnames.field = "chr",start.field = "upstreamES",
                                    end.field = "downstreamEE",strand.field = "strand")

ov<-findOverlaps(SE_region,regions_gr)
length(unique(queryHits(ov)))
length(unique(subjectHits(ov)))


#Getting the Significant Events- GE
SE_ov<-list("SE \n Event"=SE_Sig$geneSymbol,"Bound \n Gene"=unique(c(Gene$gene_name,Tag$gene_name)))
ggvenn::ggvenn(SE_ov,fill_color=c("#D5732E","#94B18E"),set_name_size=3,show_percentage=F,
                  text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 2))+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        textt=element_text(family="Arial", size=0,color="black"))
ggsave("Figures/Splicing_bound_ov.pdf",height=1.25,width=1.5)

phyper(346-1,2145,11592-2145,2516,lower.tail=F)


###
SE_sub<-SE_Sig[which(SE_Sig$geneSymbol %in% unique(c(Gene$gene_name,Tag$gene_name))),]
SE_sub$Group<-ifelse(SE_sub$IncLevelDifference>0,"Skipped","Retained")

SE_sub_tab<-data.frame(table(SE_sub$Group))
SE_sub_tab$fraction = SE_sub_tab$Freq / sum(SE_sub_tab$Freq)
SE_sub_tab$ymax = cumsum(SE_sub_tab$fraction)
SE_sub_tab$ymin = c(0, head(SE_sub_tab$ymax, n = -1))
SE_sub_tab$label_position = (SE_sub_tab$ymax + SE_sub_tab$ymin) / 2  # For text positioning
SE_sub_tab$Label<-paste(SE_sub_tab$Var1,"\n=",SE_sub_tab$Freq,sep="")

my_colors<-c("Skipped"="#FE0000","Retained"="#079BF5")
ggplot(SE_sub_tab, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect(alpha=.8) +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 1.4, y = label_position, label = Label), size = 2) +
  theme(legend.position = "none")
ggsave("Figures/Splicing_bound_ov_direction.pdf",height=1.25,width=1.5)

```

#NS-RBNS-pie
```{r}
rm(list=ls())
adapters<-read.table("NS_RBNS/SMNDC1_fa_adapter.RNAfold.table",sep="\t")
adapters$Group<-sapply(adapters$V1,function(x){strsplit(x,"_")[[1]][1]})
adapters<-adapters[c("V1","Group")]
adapters$Group<-sapply(adapters$Group,function(x){gsub(">","",x)})
adapters$GG<-ifelse(adapters$Group %in% c("Common","HA","GENO","Gene","PCBP1"),adapters$Group,"Unbound")
adapters$GG[which(adapters$GG %in% c("Common"))]<-"Both"
adapters$GG[which(adapters$GG %in% c("HA"))]<-"Anti-\nHA"
adapters$GG[which(adapters$GG %in% c("Gene"))]<-"Anti-\nSMNDC1"
adapters$GG[which(adapters$GG %in% c("PCBP1"))]<-"C-rich Seq"
adapters$GG[which(adapters$GG %in% c("GENO"))]<-"sno/snRNA"
adapters$GG[which(adapters$GG %in% c("Control"))]<-"Unbound"

#Breaking Bound and unbound
Mut<-data.frame(table(adapters$GG))
Mut$fraction = Mut$Freq / sum(Mut$Freq)
Mut$ymax = cumsum(Mut$fraction)
Mut$ymin = c(0, head(Mut$ymax, n = -1))
Mut$label_position = (Mut$ymax + Mut$ymin) / 2  # For text positioning
Mut$Label<-paste(Mut$Var1,"=",Mut$Freq,sep="")


#
Bound<-Mut[which(Mut$Var1%in% c("Anti-\nHA","Both","Anti-\nSMNDC1")),]
my_colors<-c("Anti-\nHA"="#08415C","Both"="#D26260","Anti-\nSMNDC1"="#789180")
ggplot(Bound, aes(ymax = ymax, ymin = ymin, xmax = .7, xmin = 0, fill = Var1)) +
  geom_rect() +
  coord_polar(theta = "y",start=pi*1.7) +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 1, y = label_position, label = Label), size = 2.5,family="Arial") +
  theme(legend.position = "none")
ggsave("Figures/NSRBNS_pie_Bound.pdf",width=1.5,height=1.5)

#
UnBound<-Mut[which(Mut$Var1%in% c("C-rich Seq","Unbound","sno/snRNA")),]
UnBound$Var1<-factor(UnBound$Var1,levels=c("C-rich Seq","Unbound","sno/snRNA"))
UnBound$Label<-paste(UnBound$Var1,"\n=",UnBound$Freq,sep="")
my_colors<-c("C-rich Seq"="#A379C9","Unbound"="#F5E2C8","sno/snRNA"="#00B2CA")
ggplot(UnBound, aes(ymax = ymax, ymin = ymin, xmax = .7, xmin = 0, fill = Var1)) +
  geom_rect() +
  coord_polar(theta = "y",start=pi*1.7) +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 1, y = label_position, label = Label), size = 2.5,family="Arial") +
  theme(legend.position = "none")
ggsave("Figures/NSRBNS_pie_Unbound.pdf",width=1.5,height=1.5)

```

#NS-ecdf
```{r,fig.height=1.5,fig.width=3}
rm(list=ls())

#New RBNS NS
R_val<-read.table("NS_RBNS/Counts_comined.txt",header=T)
rownames(R_val)<-R_val$ID
R_val<-R_val[,-1]
R_val_norm<-sweep(R_val,2,colSums(R_val),"/")
R_val_norm<-R_val_norm[which(!(R_val_norm$Input_SMNDC1_nsRBNS_S14_R1_001==0)),]
R_val_norm<-R_val_norm/R_val_norm$Input_SMNDC1_nsRBNS_S14_R1_001
R_val_norm$FL_125<-rowMeans(R_val_norm[c("SMNDC1_nsRBNS_125_G_S8_R1_001","SMNDC1_nsRBNS_125_M_S9_R1_001")])

R_val_norm_sub<-R_val_norm[c("FL_125")]
R_val_norm_sub$ID<-rownames(R_val_norm_sub)


#for summary files
df<-R_val
df$Identifier<-rownames(df)
df<-df[c("Identifier","Input_SMNDC1_nsRBNS_S14_R1_001","SMNDC1_nsRBNS_125_G_S8_R1_001","SMNDC1_nsRBNS_125_M_S9_R1_001")]
df<-df[which(df$Identifier %in% rownames(R_val_norm)),]
df<-merge(df,R_val_norm_sub[c("ID","FL_125")],by.x="Identifier",by.y="ID")
colnames(df)[5]<-"FL_125_Rval"

R_val_norm_sub$Group<-sapply(R_val_norm_sub$ID,function(x){strsplit(x,"_")[[1]][1]})
R_val_norm_sub$GG<-ifelse(R_val_norm_sub$Group %in% c("Common","HA","GENO","Gene","PCBP1"),R_val_norm_sub$Group,"Unbound")
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("Common"))]<-"Bound in Both"
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("HA"))]<-"Bound in Anti-HA"
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("Gene"))]<-"Bound in Anti-SMNDC1"
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("PCBP1"))]<-"C-rich Seq"
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("GENO"))]<-"sno/snRNA"
R_val_norm_sub$GG[which(R_val_norm_sub$GG %in% c("Control"))]<-"Unbound"

ggplot(R_val_norm_sub,aes(x=FL_125,color=GG))+
  stat_ecdf()+
  scale_color_manual(values = c("Bound in Anti-HA"="#08415C","Bound in Both"="#D26260","Bound in Anti-SMNDC1"="#789180",
                                "C-rich Seq"="#A379C9","Unbound"="#E3AE64","sno/snRNA"="#00B2CA"))+
  theme_classic()+
  geom_vline(xintercept = 1, linetype = "dashed")+
  lims(x=c(0,3.5))+
  labs(x="R value")+
  theme(legend.position = c(.8,.2),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Figures/NS_ecdf_125.pdf",height=2,width=3)
```






